Hypertension statistics for US adults: an open-source web application for analysis and visualization of US NHANES data

### 2022-10-23 README.Rmd
badges were behind on repo name

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/jhs-hwg/nhanes-shiny-bp/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jhs-hwg/nhanes-shiny-bp?branch=main)
[![R-CMD-check](https://github.com/jhs-hwg/nhanes-shiny-bp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jhs-hwg/nhanes-shiny-bp/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/jhs-hwg/cardioStatsUSA/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jhs-hwg/cardioStatsUSA?branch=main)
[![R-CMD-check](https://github.com/jhs-hwg/cardioStatsUSA/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jhs-hwg/cardioStatsUSA/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

### 2022-10-23 paper/manuscript.Rmd
badges were behind on repo name

<!-- TODO: make this identical to website output, including even the unreliability columns. Add footnotes to explain what column names mean -->

@@

nhanes_data %>% 
 nhanes_summarize(key = nhanes_key,
                  outcome_variable = 'demo_race',
                  group_variable = 'htn_accaha',
                  time_values = 'most_recent') %>%
 mutate(
  across(where(is.numeric), 
         .fns = table_value, 
         rspec = rspec)
 ) %>% 
 filter(statistic == 'percentage') %>% 
 select(-statistic, 
        -ends_with("reason"),
        -unreliable_status,
        -review_needed) %>% 
 flextable() %>% 
 set_header_labels(
  svy_year = 'NHANES cycle',
  htn_accaha = 'Hypertension',
  demo_race = 'Race/Ethnicity',
  estimate = 'Estimate',
  std_error = 'Standard error',
  ci_lower = 'CI lower',
  ci_upper = 'CI upper',
  n_obs = 'N observations'
 ) %>% 
 theme_box() %>% 
 width(width = 1) %>% 
 align(align = 'center', part = 'all') %>% 
 align(j = 1, align = 'center', part = 'all')

>>>>

@@

nhanes_data %>% 
 nhanes_summarize(key = nhanes_key,
                  outcome_variable = 'demo_race',
                  group_variable = 'htn_accaha',
                  time_values = 'most_recent') %>%
 mutate(
  across(where(is.numeric), 
         .fns = table_value, 
         rspec = rspec)
 ) %>% 
 filter(statistic == 'percentage') %>% 
 flextable() %>% 
 theme_box() %>% 
 width(width = 0.5) %>% 
 align(align = 'center', part = 'all') %>% 
 align(j = 1, align = 'center', part = 'all') %>% 
 add_footer_lines(
  values = "Table format is identical to the web application's output."
 ) %>% 
 add_footer_lines(
  values = "svy_year indicates the NHANES cycle"
 ) %>% 
 add_footer_lines(
  values = "htn_accaha indicates hypertension status." 
 ) %>% 
 add_footer_lines(
  values = "demo_race indicates the race subgroup."
 ) %>% 
 add_footer_lines(
  values = "statistic indicates the type of statistic computed."
 ) %>% 
 add_footer_lines(
  values = "estimate is the point estimate of the given statistic"
 ) %>% 
 add_footer_lines(
  values = "std_error is the standard error for estimate"
 ) %>% 
 add_footer_lines(
  values = "ci_lower is the lower bound of a 95% confidence interval for estimate"
 ) %>% 
 add_footer_lines(
  values = "ci_upper is the upper bound of a 95% confidence interval for estimate"
 ) %>% 
 add_footer_lines(
  values = "n_obs is the number of observations (unweighted) used for computations"
 ) %>% 
 add_footer_lines(
  values = "unreliable_status is TRUE if the result is unreliable, FALSE otherwise"
 ) %>% 
 add_footer_lines(
  values = "unreliable_reason is blank if the result is reliable, and lists reason(s) for unreliability otherwise"
 ) %>% 
 add_footer_lines(
  values = "review_needed is TRUE if the result should be reviewed, FALSE otherwise"
 ) %>% 
 add_footer_lines(
  values = "review_reason is blank if the result does not require review, and lists reason(s) for requiring review otherwise"
 )
